Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-02-24 manuscripts/TCS2022/tcs2022.tex
small changes

% Mention the extensions for the journal version
Herein we revise and extend our previous work in~\cite{DBLP:conf/cmsb/TrinhBHS22} as follows.
First, more formal definitions are given and the existing proofs are made more detailed.
In particular, an updated proof provides another way to prove the independence of trap spaces of a Boolean network on its update scheme, which was originally proved in~\cite{klarner2015computing}.
Second, we showcase a theoretical application of the connection between trap spaces in Boolean networks and conflict-free siphons in Petri nets.
Third, beyond the proposed ASP method implementing the alternative approach~\cite{DBLP:conf/cmsb/TrinhBHS22}, we propose several other possible methods for computing minimal trap spaces using Maximum Satisfiability (MaxSAT), Constraint Programming (CP), and Integer Linear Programming (ILP).
Fourth, we discuss in detail how to compute several special types of trap spaces in a Boolean network.
%Fifth, we present the idea for using our Petri net approach to handle the problem of inconsistent and incomplete data in modeling biological systems.
Fifth, regarding the implementation, we have developed a new converter that directly reads a \texttt{.bnet} file and builds the Petri net encoding, instead of using the \texttt{PNML} conversion of \texttt{bioLQM}~\cite{DBLP:conf/cmsb/TrinhBHS22}.
Finally, we conduct a more comprehensive benchmark on more real-world models from various sources and randomly generated models to evaluate all the proposed methods (the benchmark conducted in~\cite{DBLP:conf/cmsb/TrinhBHS22} considers only real-world models).

@@

We shall briefly recall here some preliminaries on Boolean networks related to trap spaces and Petri nets.
%In the case of multi-level logical models, an encoding into a Boolean network is always possible~\cite{Didier2011}.
\vangiang{Remove this statement because there is not sure if the encoded Boolean network preserves the trap spaces of the original multi-level logical model.}

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.85}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & - & - & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $>1000$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & - & - & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & - & - & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & - & - & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $>1000$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & - & - & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & - & - & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & - & - & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.8}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & - & - & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & - & - & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & - & - & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & - & - & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & - & - & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & - & - & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & - & - & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & - & - & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & - & - & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $>1000$ & N/A & 0.11 & 0.36 & 0.17 & - & - & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & - & - & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & - & - & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $>1000$ & N/A & \textbf{DNF} & 0.50 & 0.34 & - & - & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & - & - & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & - & - & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $>1000$ & N/A & 0.09 & 0.55 & 0.37 & - & - & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $>1000$ & N/A & \textbf{107.57} & 0.76 & 0.56 & - & - & 0.16 \\

    \midrule % 100 <= n < 200
     \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & 78 & \textbf{56.81} & \textbf{4.25} & 0.23 & 0.17 & - & - & 0.19 \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & 82 & \textbf{DNF} & \textbf{14.01} & 0.27 & 0.20 & - & - & 0.25 \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & $>1000$ & N/A & 0.54 & 1.09 & 0.84 & - & - & 0.27 \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & $>1000$ & N/A & 0.16 & 1.07 & 1.06 & - & - & 0.16 \\
    \rownb & angiofull~\cite{Weinstein2017} & 142 & $>1000$ & N/A & 0.17 & 1.06 & 0.88 & - & - & 0.23 \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & 492 & \textbf{DNF} & \textbf{11.28} & 0.78 & 0.69 & - & - & 0.35 \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & $>1000$ & N/A & \textbf{DNF} & 1.43 & 1.55 & - & - & 0.19 \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & $>1000$ & N/A & \textbf{13.58} & 1.76 & 1.51 & - & - & 0.27 \\

    \midrule % 200 <= n
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & $>1000$ & N/A & 1.13 & 1.47 & 1.43 & - & - & 0.31 \\
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & $>1000$ & N/A & \textbf{DNF} & 1.52 & 2.26 & - & - & 0.35 \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & $>1000$ & N/A & \textbf{4.99} & NM & 1.96 & - & - & 0.28 \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & $>1000$ & N/A & 0.42 & 2.36 & \textbf{4.91} & - & - & 0.44 \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & $>1000$ & N/A & \textbf{DNF} & 2.56 & \textbf{5.62} & - & - & 0.46 \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & $>1000$ & N/A & 0.36 & 2.99 & \textbf{4.81} & - & - & 0.37 \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & $>1000$ & N/A & \textbf{DNF} & NM & \textbf{18.21} & - & - & 0.79 \\

>>>>

% Mention the extensions for the journal version
Herein we revise and extend our previous work in~\cite{DBLP:conf/cmsb/TrinhBHS22} as follows.
First, more formal definitions are given and the existing proofs are made more detailed.
In particular, an updated proof provides another way to prove the independence of trap spaces of a Boolean network on its update scheme, which was originally proved in~\cite{klarner2015computing}.
Second, we showcase a theoretical application of the connection between trap spaces in Boolean networks and conflict-free siphons in Petri nets.
Third, beyond the proposed ASP method implementing the alternative approach~\cite{DBLP:conf/cmsb/TrinhBHS22}, we propose several other possible methods for computing minimal trap spaces using Maximum Satisfiability (MaxSAT), Constraint Programming (CP), and Integer Linear Programming (ILP).
Fourth, we discuss in detail how to compute several special types of trap spaces in a Boolean network.
Besides minimal trap spaces, these special types also play crucial roles in analyzing Boolean networks~\cite{Rozum2021}.
%Fifth, we present the idea for using our Petri net approach to handle the problem of inconsistent and incomplete data in modeling biological systems.
Fifth, regarding the implementation, we have developed a new converter that directly reads a \texttt{.bnet} file and builds the Petri net encoding, instead of using the \texttt{PNML} conversion of \texttt{bioLQM}~\cite{DBLP:conf/cmsb/TrinhBHS22}.
Finally, we conduct a more comprehensive benchmark on more real-world models from various sources and randomly generated models to evaluate all the proposed methods (the benchmark conducted in~\cite{DBLP:conf/cmsb/TrinhBHS22} considers only dozens of representative real-world models).

@@

We shall briefly recall here some preliminaries on Boolean networks related to trap spaces and Petri nets.
%In the case of multi-level logical models, an encoding into a Boolean network is always possible~\cite{Didier2011}.
%\vangiang{Remove this statement because there is not sure if the encoded Boolean network preserves the trap spaces of the original multi-level logical model.}

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.9}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & - & - & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $1000^+$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & - & - & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & - & - & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & - & - & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $1000^+$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & - & - & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & - & - & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & - & - & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.8}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & - & - & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & - & - & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & - & - & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & - & - & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & - & - & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & - & - & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & - & - & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & - & - & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & - & - & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $1000^+$ & N/A & 0.11 & 0.36 & 0.17 & - & - & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & - & - & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & - & - & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $1000^+$ & N/A & \textbf{DNF} & 0.50 & 0.34 & - & - & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & - & - & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & - & - & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $1000^+$ & N/A & 0.09 & 0.55 & 0.37 & - & - & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $1000^+$ & N/A & \textbf{107.57} & 0.76 & 0.56 & - & - & 0.16 \\

    \midrule % 100 <= n < 200
     \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & 78 & \textbf{56.81} & \textbf{4.25} & 0.23 & 0.17 & - & - & 0.19 \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & 82 & \textbf{DNF} & \textbf{14.01} & 0.27 & 0.20 & - & - & 0.25 \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & $1000^+$ & N/A & 0.54 & 1.09 & 0.84 & - & - & 0.27 \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & $1000^+$ & N/A & 0.16 & 1.07 & 1.06 & - & - & 0.16 \\
    \rownb & angiofull~\cite{Weinstein2017} & 142 & $1000^+$ & N/A & 0.17 & 1.06 & 0.88 & - & - & 0.23 \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & 492 & \textbf{DNF} & \textbf{11.28} & 0.78 & 0.69 & - & - & 0.35 \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & $1000^+$ & N/A & \textbf{DNF} & 1.43 & 1.55 & - & - & 0.19 \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & $1000^+$ & N/A & \textbf{13.58} & 1.76 & 1.51 & - & - & 0.27 \\

    \midrule % 200 <= n
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & $1000^+$ & N/A & 1.13 & 1.47 & 1.43 & - & - & 0.31 \\
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & $1000^+$ & N/A & \textbf{DNF} & 1.52 & 2.26 & - & - & 0.35 \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & $1000^+$ & N/A & \textbf{4.99} & NM & 1.96 & - & - & 0.28 \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & $1000^+$ & N/A & 0.42 & 2.36 & \textbf{4.91} & - & - & 0.44 \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & $1000^+$ & N/A & \textbf{DNF} & 2.56 & \textbf{5.62} & - & - & 0.46 \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & $1000^+$ & N/A & 0.36 & 2.99 & \textbf{4.81} & - & - & 0.37 \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & $1000^+$ & N/A & \textbf{DNF} & NM & \textbf{18.21} & - & - & 0.79 \\
